---
title: "P-STEM Wave 2 Target Codebook"
author: "Linh Nguyen"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 4
    code_folding: 'hide'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(digits = 3)

libraries <- c("rio",          # import export
               "ggplot2",      # plots
               "dplyr",        # general wrangling
               "likert",       # likert plot
               "kableExtra",   # session info
               "labelled")     # value labels

lapply(libraries, require, character.only = TRUE)
```

# I. Meta Data

This [codebook](https://rpubs.com/nguyenllpsych/pstem_target2) includes only quantitative scales. Qualitative responses collected for the following scales are not included here:

- Major/Career Pathway Narrative
- Deviation Narrative
- Pride Narrative
- Twenty Statements Test (Kuhn & McPartland, 1954)

In addition, the following demographic data were collected but not shown here:

- Sexual orientation (open ended)
- Major (open ended)
- Potential major change (open ended)

```{r session-info, results = "hold"}
# list of loaded packages and versions
si <- devtools::session_info()[[2]]
rownames(si) <- NULL
si %>% 
  select(package, loadedversion, date, source) %>% 
  
  #red bold the called packages
  mutate(package = 
           cell_spec(package, 
                     color = ifelse(package %in% libraries, "red", "black"),
                     bold = ifelse(package %in% libraries, TRUE, FALSE))) %>% 
  knitr::kable(escape = F, caption = "All loaded packages. 
               Bolded in red are those loaded explicitly with 
               <code>library()</code>") %>% 
  kable_styling() %>% 
  scroll_box(height = "300px")
```

```{r load-data}
# load scored data
data <- readRDS(file = "../PSTEM_Wave_2_SCORED_2023-03-29.RData")

# load dictionary
dict <- read.csv(file = "../PSTEM_Data-Dictionary_Wave_2_Target.csv")
```

# II. Demographics

There are a total of `r nrow(data)` participants in wave 2, and `r data %>% select(-one_of(c("gender_f","race_f"))) %>% complete.cases() %>% sum()` participants with non-missing data.

```{r demo}
# gender
ggplot(data[which(!is.na(data$gender_f)),], 
       aes(factor(gender_f,
                  levels = c("woman", "man"),
                  labels = c("woman", "man")))) + 
  geom_bar(fill = c("#f1c232", "#710c0c")) + 
  geom_text(stat='count', aes(label=..count..), vjust = -1) + 
  labs(
    title = "Count of Gender",
    x = NULL
  ) +
  ylim(0, 150) +
  theme_classic()

# race
ggplot(data[which(!is.na(data$race_f)),], 
       aes(factor(race_f,
                  levels = c("asian", "black", "hispanic", "mixed"),
                  labels = c("asian", "black", "hispanic", "mixed")))) + 
  geom_bar(fill = "#710c0c") + 
  geom_text(stat='count', aes(label=..count..), vjust = -1) + 
  labs(
    title = "Count of racial/ethnic groups",
    x = NULL
  ) +
  ylim(0, 125) +
  theme_classic()
```

# III. STEM Scales

## STEM Measures (Chemers et al., 2011)

```{r stem, fig.width=11, fig.height = 7}
# stem-se
stemse_items <- dict %>%
  filter(grepl(pattern = "stemse", x = variable)) %>%
  pull(variable)
stemse_items <- data %>%
  select(all_of(stemse_items)) 
names(stemse_items) <- var_label(stemse_items)
stemse_items <- stemse_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Not at all confident", "To a small extent", 
                      "To some extent", "To a large extent", 
                      "Absolutely confident"))
  })
plot(likert(stemse_items)) + 
  theme(axis.text = element_text(size=12)) +
  labs(title = "STEM Self-Efficacy")

# stemment-sm
stemment_sm_items <- c("stemment_1","stemment_2","stemment_3","stemment_4",
                       "stemment_5","stemment_6","stemment_7")
stemment_sm_items <- data %>%
  select(all_of(stemment_sm_items)) 
names(stemment_sm_items) <- var_label(stemment_sm_items)
stemment_sm_items <- stemment_sm_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Not at all", "To a small extent", 
                      "To some extent", "To a large extent", 
                      "To a very large extent"))
  })
plot(likert(stemment_sm_items)) + 
  theme(axis.text = element_text(size=12)) +
  labs(title = "STEM Socioemotional Mentoring")

# stemment-im
stemment_im_items <- c("stemment_8","stemment_9","stemment_10",
                       "stemment_11","stemment_12","stemment_13")
stemment_im_items <- data %>%
  select(all_of(stemment_im_items)) 
names(stemment_im_items) <- var_label(stemment_im_items)
stemment_im_items <- stemment_im_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Not at all", "To a small extent", 
                      "To some extent", "To a large extent", 
                      "To a very large extent"))
  })
plot(likert(stemment_im_items)) + 
  theme(axis.text = element_text(size=12)) +
  labs(title = "STEM Instrumental Mentoring")

# stemidco-id
stemidco_id_items <- c("stemidco_1","stemidco_2","stemidco_3",
                       "stemidco_4","stemidco_5","stemidco_6")
stemidco_id_items <- data %>%
  select(all_of(stemidco_id_items)) 
names(stemidco_id_items) <- var_label(stemidco_id_items)
stemidco_id_items <- stemidco_id_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Strongly Disagree", "Somewhat Disagree", 
                      "Neutral", "Somewhat Agree", "Strongly Agree"))
  })
plot(likert(stemidco_id_items)) + 
  theme(axis.text = element_text(size=12)) +
  labs(title = "STEM Identity as a Scientist")

# stemidco-co
stemidco_co_items <- c("stemidco_9","stemidco_10","stemidco_11",
                       "stemidco_12","stemidco_13","stemidco_14","stemidco_15")
stemidco_co_items <- data %>%
  select(all_of(stemidco_co_items)) 
names(stemidco_co_items) <- var_label(stemidco_co_items)
stemidco_co_items <- stemidco_co_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Strongly Disagree", "Somewhat Disagree", 
                      "Neutral", "Somewhat Agree", "Strongly Agree"))
  })
plot(likert(stemidco_co_items)) + 
  theme(axis.text = element_text(size=12)) +
  labs(title = "STEM Commitment to a Science Career")
```

## STEM Identity Integration (Walker & Syed, 2012)

```{r stemidco-emi, fig.width=11, fig.height = 7}
# items
stemidco_emi_items <- c("stemidco_7","stemidco_8")
stemidco_emi_items <- data %>%
  select(all_of(stemidco_emi_items)) 
names(stemidco_emi_items) <- var_label(stemidco_emi_items)
stemidco_emi_items <- stemidco_emi_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Strongly Disagree", "Somewhat Disagree", 
                      "Neutral", "Somewhat Agree", "Strongly Agree"))
  })
plot(likert(stemidco_emi_items)) + 
  theme(axis.text = element_text(size=12)) +
  labs(title = "STEM Ethnicity-Major Integration")
```


# IV. Identity and Wellbeing Scales
## Utrecht Management of Identity Commitments - Education Domain (Crocetti et al., 2008) 

```{r umics, fig.width=11, fig.height = 5}
# items
umics_variables <- c("education commitment", "education in-depth exploration", 
                     "education reconsideration of commitment")
for(var in umics_variables){
  items <- dict %>% 
    filter(scale == var) %>% 
    pull(variable)
  items <- data %>%
    select(all_of(items)) 
  names(items) <- var_label(items)
  items <- items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Strongly Disagree", "Somewhat Disagree", 
                      "Neutral", "Somewhat Agree", "Strongly Agree"))
  })
  print(plot(likert(items),
       main = var) + 
    theme(axis.text = element_text(size=12)) +
    labs(title = var))
}
```

## Eriksonian Psychosocial Stage Inventory - Identity Subscale (Rosenthal et al., 1981)

```{r epsi, fig.width=11}
# epsi coherence
epsi_coh_items <- c("epsi_2","epsi_4","epsi_5","epsi_6","epsi_8","epsi_9")
epsi_coh_items <- data %>%
  select(all_of(epsi_coh_items)) 
names(epsi_coh_items) <- var_label(epsi_coh_items)
epsi_coh_items <- epsi_coh_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Strongly Disagree", "Somewhat Disagree", 
                      "Neutral", "Somewhat Agree", "Strongly Agree"))
  })
plot(likert(epsi_coh_items)) + 
  theme(axis.text = element_text(size=12)) +
  labs(title = "Identity Coherence")

# epsi confusion
epsi_con_items <- c("epsi_1","epsi_3","epsi_7","epsi_10","epsi_11","epsi_12")
epsi_con_items <- data %>%
  select(all_of(epsi_con_items)) 
names(epsi_con_items) <- var_label(epsi_con_items)
epsi_con_items <- epsi_con_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Strongly Disagree", "Somewhat Disagree", 
                      "Neutral", "Somewhat Agree", "Strongly Agree"))
  })
plot(likert(epsi_con_items)) + 
  theme(axis.text = element_text(size=12)) +
  labs(title = "Identity Confusion")
```

## Multigroup Ethnic Identity Measure (Roberts et al., 1999) 

```{r meim, fig.width=11}
# meim exploration
meim_ex_items <- c("meim_1", "meim_2", "meim_4", "meim_8", "meim_10")
meim_ex_items <- data %>%
  select(all_of(meim_ex_items)) 
names(meim_ex_items) <- var_label(meim_ex_items)
meim_ex_items <- meim_ex_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Strongly Disagree", "Somewhat Disagree", 
                      "Neutral", "Somewhat Agree", "Strongly Agree"))
  })
plot(likert(meim_ex_items)) + 
  theme(axis.text = element_text(size=12)) +
  labs(title = "Ethnic Identity Exploration")

# meim commitment
meim_co_items <- c("meim_3", "meim_5", "meim_6", "meim_7", 
                   "meim_9", "meim_11", "meim_12")
meim_co_items <- data %>%
  select(all_of(meim_co_items)) 
names(meim_co_items) <- var_label(meim_co_items)
meim_co_items <- meim_co_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Strongly Disagree", "Somewhat Disagree", 
                      "Neutral", "Somewhat Agree", "Strongly Agree"))
  })
plot(likert(meim_co_items)) + 
  theme(axis.text = element_text(size=12)) +
  labs(title = "Ethnic Identity Commitment")
```

## Satisfaction with Life (Diener et al., 1985)

```{r swls, fig.width=11}
swls_items <- c("swls_1","swls_2","swls_3","swls_4","swls_5")
swls_items <- data %>%
  select(all_of(swls_items)) 
names(swls_items) <- var_label(swls_items)
swls_items <- swls_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:7),
           labels = c("Strongly Disagree", "Disagree", "Slightly Disagree",
                      "Neither Agree nor Disagree", "Slightly Agree",
                      "Agree", "Strongly Agree"))
  })
plot(likert(swls_items)) + 
  theme(axis.text = element_text(size=12)) +
  labs(title = "Satisfaction with Life")
```

## Self-concept clarity (Campbell et al. 1996) 

```{r scc, fig.width=11, fig.height=15}
ssc_items <- c("ssc_1", "ssc_2", "ssc_3", "ssc_4", "ssc_5", "ssc_6", 
                "ssc_7", "ssc_8", "ssc_9", "ssc_10", "ssc_11", "ssc_12")
ssc_items <- data %>%
  select(all_of(ssc_items)) 
names(ssc_items) <- var_label(ssc_items)
ssc_items <- ssc_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Strongly Disagree", "Somewhat Disagree", 
                      "Neutral", "Somewhat Agree", "Strongly Agree"))
  })
plot(likert(ssc_items)) + 
  theme(axis.text = element_text(size=12))
```

## Social Support from Family and Friends (Procidano & Heller, 1983) 

```{r ss, fig.width=11, fig.height = 15}
ss_variables <- c("social support from friends", "social support from family")
for(var in ss_variables){
  items <- dict %>% 
    filter(scale == var) %>% 
    pull(variable)
  items <- data %>%
    select(all_of(items)) 
  names(items) <- var_label(items)
  items <- items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Strongly Disagree", "Somewhat Disagree", 
                      "Neutral", "Somewhat Agree", "Strongly Agree"))
  })
  print(plot(likert(items),
       main = var) + 
    theme(axis.text = element_text(size=12)) +
    labs(title = var))
}
```


# V. Personality Scales
## The Personality Inventory for DSM-5—Brief Form (Krueger et al., 2013)

```{r pidv, fig.width=11}
pid_variables <- c("disinhibition", "detachment", "psychoticism", 
                   "negative", "antagonism")
for(var in pid_variables){
  items <- dict %>% 
    filter(scale == var) %>% 
    pull(variable)
  items <- data %>%
    select(all_of(items)) 
  names(items) <- var_label(items)
  items <- items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:4),
           labels = c("Very False or Often False", "Sometimes or Somewhat False", 
                      "Sometimes or Somewhat True", "Very True or Often True"))
  })
  print(plot(likert(items),
       main = var) + 
    theme(axis.text = element_text(size=12)) +
    labs(title = paste0("PID-5 Variable: ", var)))
}
```


# VI. Cognitive Abilities and Interests Scales
## Scientific Reasoning Task (Drummond & Fischhoff, 2017)

```{r srt, fig.width=11, fig.height = 23}
# items
srs_items <- c("srs_1_scored", "srs_2_scored", "srs_3_scored", "srs_4_scored", 
               "srs_5_scored", "srs_6_scored", "srs_7_scored", "srs_8_scored", 
               "srs_9_scored", "srs_10_scored", "srs_11_scored")
srs_items <- data %>%
  select(all_of(srs_items)) 
srs_ori <- c("srs_1", "srs_2", "srs_3", "srs_4", 
             "srs_5", "srs_6", "srs_7", "srs_8", 
             "srs_9", "srs_10", "srs_11")
srs_ori <- data %>%
  select(all_of(srs_ori)) 
names(srs_items) <- var_label(srs_ori)
srs_items <- srs_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(0,1),
           labels = c("Incorrect", "Correct"))
  })
plot(likert(srs_items)) + 
  theme(axis.text = element_text(size=12))
```

## Locus of Control (Cote, 1997)

```{r loc, fig.width=11, fig.height = 7}
# items
loc_int_items <- dict %>% 
        filter(scale == "internal") %>% 
        pull(variable)
loc_int_items <- data %>%
  select(all_of(loc_int_items)) 
names(loc_int_items) <- var_label(loc_int_items)
loc_int_items <- loc_int_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Strongly Disagree", "Somewhat Disagree", 
                      "Neutral", "Somewhat Agree", "Strongly Agree"))
  })
plot(likert(loc_int_items)) + 
  theme(axis.text = element_text(size=12)) + 
  labs(title = "Internal Locus of Control")
```

## Educational Public Regard

```{r epr, fig.width=11, fig.height = 7}
# items
epr_items <- dict %>% 
        filter(scale == "public regard") %>% 
        pull(variable)
epr_items <- data %>%
  select(all_of(epr_items)) 
names(epr_items) <- var_label(epr_items)
epr_items <- epr_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Strongly Disagree", "Somewhat Disagree", 
                      "Neutral", "Somewhat Agree", "Strongly Agree"))
  })
plot(likert(epr_items)) + 
  theme(axis.text = element_text(size=12)) +
  labs(title = "Educational Public Regard")
```

## Theory of Intelligence (Dweck, 2000)

```{r toi, fig.width=11, fig.height = 7}
# items
toi_items <- dict %>% 
        filter(scale == "growth") %>% 
        pull(variable)
toi_items <- data %>%
  select(all_of(toi_items)) 
names(toi_items) <- var_label(toi_items)
toi_items <- toi_items %>%
  mutate_all(.funs = function(x){
    factor(x, levels = c(1:5),
           labels = c("Strongly Disagree", "Somewhat Disagree", 
                      "Neutral", "Somewhat Agree", "Strongly Agree"))
  })
plot(likert(toi_items)) + 
  theme(axis.text = element_text(size=12)) +
  labs(title = "Growth Mindset")
```

